My title

### 2024-11-28 paper/paper.qmd
fixed alignment issue with model

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Hyunje Park
thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating). Special thanks to Rohan Alexander for his help!"
date: today
date-format: long
abstract: "This paper examines the rating of childrens' books using the . By using logistic regression and data from the Alex Cookson (CITATION), I analyzed the relationship between various characteristics of a childrens' book, and whether or not it influenced if the book had a high rating or not. The insight from this research not only clarify what makes a high rated childrens' book so high rated, but also enhance future authors to push the boundaries of their literature"
format: pdf
number-sections: true
bibliography: references.bib
---

@@

@@

@@

@@

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Hyunje Park
thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating). Special thanks to Rohan Alexander for his help!"
date: today
date-format: long
abstract: "This paper examines the rating of childrens' books using the . By using a Bayesian logistic regression and data from the Alex Cookson (CITATION), I analyzed the relationship between various characteristics of a childrens' book, and whether or not it influenced if the book had a high rating or not. The insight from this research not only clarify what makes a high rated childrens' book so high rated, but also enhance future authors to push the boundaries of their literature."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(here)
library(rstanarm)
library(modelsummary)
library(ggplot2)
library(knitr)

@@

This study employed a Bayesian logistic regression model to analyze the relationship between Children's book's "highly-rated" status and the characteristic of the book. The model is as follows:

\begin{align} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \label{eq1} \\
\mbox{logit}(\pi_i) &= \beta_0 + \beta_1 \times \mbox{pages$_i$} \\
&\quad + \beta_2 \times \mbox{rating\_count$_i$} + \beta_3 \times \mbox{publish\_year$_i$} \\
&\quad + \beta_4 \times \mbox{coverEbook$_i$} + \beta_5 \times \mbox{coverKindleEdition$_i$} \\
&\quad + \beta_6 \times \mbox{coverBoardBook$_i$} + \beta_7 \times \mbox{coverHardcover$_i$} \\
&\quad + \beta_8 \times \mbox{coverPaperback$_i$} \label{eq2} \\
\beta_0 &\sim \mbox{Normal}(0, 2.5) \label{eq3} \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \label{eq4} \\
\beta_2 &\sim \mbox{Normal}(0, 2.5) \label{eq5}\\
\beta_3 &\sim \mbox{Normal}(0, 2.5) \label{eq6}\\
\beta_4 &\sim \mbox{Normal}(0, 2.5) \label{eq7}\\
\beta_5 &\sim \mbox{Normal}(0, 2.5) \label{eq8}\\
\beta_6 &\sim \mbox{Normal}(0, 2.5) \label{eq9}\\
\beta_7 &\sim \mbox{Normal}(0, 2.5) \label{eq10}\\
\beta_8 &\sim \mbox{Normal}(0, 2.5) \label{eq11}
\end{align}

## Prior Distribution

The rstanarm package (CITATION) was used in order to run the regression model mentioned above. The default priors of the rstanarm package was used (CITATION). These default priors are designed to be weakly informative, meaning they provide enough information to regularize the model and prevent extreme estimates, while being flexible to let the data drive the inference. By default, priors for regression coefficients are centered around 0 with a standard deviation of 2.5, which is shown in equations (Equation LIST).

## Model Justification

The predictor variables shown in (LIST HERE) were chosen due to the number of studies regarding their influence on ratings of books.

More specifically, I expect that

@@

After running the regression model above, we receive the coefficient values showcased in Table X.

@@

model_file <- readRDS(file = here::here("models/model.rds"))
